Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-16 journal paper/content/sec-bg.tex
fix typo

\item Adaptive-exploration algorithms \emph{can} have an even better regret rate: $\BIR(t) = \tildeO\rbr{ t^{-1/2} } $, \eg this holds for Successive Elimination \citep{EvenDar-icml06}. Any optimal MAB algorithm such as Thompson Sampling and UCB1 enjoys this regret rate ``on average", because it satisfies 
        $\BReg(T)\leq \tildeO(sqrt{T})$.
    Put differently, if such algorithm satisfies 
        $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$
    for all $t$ and some $\gamma>0$, then $\gamma \leq \nicefrac{1}{2}$.
    That said, a uniform upper bound on $\BIR$ of Thompson Sampling or UCB1 is not known, to the best of our knowledge.

>>>>

\item Adaptive-exploration algorithms \emph{can} have an even better regret rate: $\BIR(t) = \tildeO\rbr{ t^{-1/2} } $, \eg this holds for Successive Elimination \citep{EvenDar-icml06}. Any optimal MAB algorithm such as Thompson Sampling and UCB1 enjoys this regret rate ``on average", because it satisfies 
        $\BReg(T)\leq \tildeO(\sqrt{T})$.
    Put differently, if such algorithm satisfies 
        $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$
    for all $t$ and some $\gamma>0$, then $\gamma \leq \nicefrac{1}{2}$.
    That said, a uniform upper bound on $\BIR$ of Thompson Sampling or UCB1 is not known, to the best of our knowledge.
